Large Linear Multi-output Gaussian Process Learning

### 2017-03-31 paper/paper.tex
added paper auxiliary files (now compiles)

\begin{table}[!ht]
  \caption{The runtime in seconds for solving $K\Tx=\Ty$ for a random kernel $K$ constructed as in Section~\ref{empirical-rep} using MINRES for each of the kernel representations. For comparison, the \textsc{chol} representation is wallclock time to compute the Cholesky decomposition of the matrix, which must be constructed, and use this decomposition to invert the system. We averaged over five runs. In every run, we use $n=5,000$ simulated data points, $\texttt{mix}$ kernels, and $\epsilon=0.1$.
}
\label{complement}
\vskip 0.15in
\begin{center}
\begin{small}
  \begin{sc}
\begin{tabular}{|ccc|cccc|}
  \hline
  \abovespace\belowspace
  $D$ & $R$ & $Q$ & {chol} & {sum} & {bt} & {slfm}\\
\hline
  \abovespace
 $ 2 $ & $ 2 $ & $ 10 $ & $ 40.71 $ & $ 38.13 $ & $ \textbf{7.83} $ & $ 59.53 $ \\ 
 $ 10 $ & $ 1 $ & $ 10 $ & $ 37.69 $ & $ 33.15 $ & $ 16.39 $ & $ \textbf{11.59} $ \\ 
 $ 10 $ & $ 10 $ & $ 1 $ & $ 11.19 $ & $ \textbf{0.784} $ & $ 2.458 $ & $ 1.138 $

  \belowspace \\

  \hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

@@

\begin{table}[!ht]
  \caption{Average predictive performance and training time over $10$ runs for LLGP and COGP on the FX2007 dataset. Parenthesized values are standard error. LLGP was run with LMC set to $Q=1$, $R=2$, and $238$ interpolating points. COGP used a $Q=2$ kernel with $100$ inducing points}
\label{fx2007-tbl}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{|l|cc|}
\hline
  \abovespace\belowspace
  Metric & LLGP Q1R2 & COGP\\
\hline
\abovespace
  SMSE & $0.2107$ & $0.2444$ \\
  NLPD & $-3.6074$ & $10.9142$ \\
  Seconds & $65$ ($3$) & $291$ ($3$)
\belowspace\\
\hline
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

@@

We use the COGP parameters that were set by default in the code provided by the authors.\footnote{\url{https://github.com/trungngv/cogp}, commit \texttt{3b07f621ff11838e89700cfb58d26ca39b119a35}. The weather dataset was run on 1500 iterations, mini-batch size 1000.} LLGP was run with the same parameters as in FX2007, simulating the SLFM model. We tested LLGP models on different numbers of interpolating points $m$. Both LLGP and COGP were run $10$ times, and average results are reported.

LLGP performed slightly worse than COGP in SMSE: its SMSE is $0.0907$ with compared to COGP's $0.0812$. However, both NLPD and runtime indicate significant improvements. The COGP result on $200$ inducing points had an NLPD of $99.7$ and runtime of $1342$ seconds. Varying the number of interpolating points $m$ from $400$ to $1000$ constructs a tradeoff frontier between increases in $m$ and NLPD decrease at the cost of additional runtime (Fig.~\ref{fig:llgpweather}). While NLPD improvement diminishes as $m$ increases, LLGP is still an improvement compared to COGP for a range of $m$ by an order of magnitude in runtime and almost two orders of magnitude for NLPD.

\begin{figure}[!ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{m_time_nlpd.eps}}
\caption{Average and standard error of NLPD and runtime of the SLFM model on LLGP across over varying interpolating points. Every setting was run 50 times.}
\label{fig:llgpweather}
\end{center}
\vskip -0.2in
\end{figure}
\section{Conclusion}\label{conclusion}

>>>>

\begin{table}[!ht]
  \caption{The runtime in seconds for solving $K\Tx=\Ty$ for a random kernel $K$ constructed as in Section~\ref{empirical-rep} using MINRES for each of the kernel representations. For comparison, the \textsc{chol} representation is wallclock time to compute the Cholesky decomposition of the matrix, which must be constructed, and use this decomposition to invert the system. We averaged over five runs. In every run, we use $n=5,000$ simulated data points, $\texttt{mix}$ kernels, and $\epsilon=0.1$.
}
\label{complement}
\vskip 0.15in
\begin{center}
  \begin{small}
    \input{representation.tex}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

@@

\begin{table}[!ht]
  \caption{Average predictive performance and training time over $10$ runs for LLGP and COGP on the FX2007 dataset. Parenthesized values are standard error. LLGP was run with LMC set to $Q=1$, $R=2$, and $238$ interpolating points. COGP used a $Q=2$ kernel with $100$ inducing points}
\label{fx2007-tbl}
\vskip 0.15in
\begin{center}
  \begin{small}
    \begin{sc}
      \input{results_fx2007.tex}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

@@

We use the COGP parameters that were set by default in the code provided by the authors.\footnote{\url{https://github.com/trungngv/cogp}, commit \texttt{3b07f621ff11838e89700cfb58d26ca39b119a35}. The weather dataset was run on 1500 iterations, mini-batch size 1000.} LLGP was run with the same parameters as in FX2007, simulating the SLFM model. We tested LLGP models on different numbers of interpolating points $m$.

\begin{table}[!ht]
  \caption{Average predictive performance and training time over $10$ runs for LLGP and COGP on the weather dataset. Parenthesized values are standard error. Both LLGP and COGP trained the SLFM model. We show LLGP with $500$ and $1000$ interpolating points and COGP with $200$ inducing points.}
\label{weather-tbl}
\vskip 0.15in
\begin{center}
  \begin{small}
    \begin{sc}
      \input{results_weather.tex}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

LLGP performed slightly worse than COGP in SMSE, but both NLPD and runtime indicate significant improvements (Tbl.~\ref{weather-tbl}). Varying the number of interpolating points $m$ from $500$ to $1000$ constructs a tradeoff frontier between increases in $m$ and NLPD decrease at the cost of additional runtime (Fig.~\ref{fig:llgpweather}). While NLPD improvement diminishes as $m$ increases, LLGP is still an improvement compared to COGP for a range of $m$ by an order of magnitude in runtime and almost two orders of magnitude for NLPD.

\begin{figure}[!ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{m_time_nlpd.eps}}
\caption{Average and standard error of NLPD and runtime of the SLFM model on LLGP across over varying interpolating points. Every setting was run 10 times.}
\label{fig:llgpweather}
\end{center}
\vskip -0.2in
\end{figure}
\section{Conclusion}\label{conclusion}
